Legacy Data Confounds Modern Genomics Studies

### 2018-04-20 Draft3.tex
updated SFS. Removed HWE sites and fixed bin size issue

\author[1]{Luke Anderson-Trocm\'e}
\author[1,2]{Simon Gravel}

@@

\corr{luke.anderson-trocme@mail.mcgill.ca}{LAT}

@@

			\section{Introduction}
	\subsection{Big Data}			
The last 5 years has seen an increase in the number of individuals genotyped through private companies or medical research cohorts. 
Larger sample sizes allow researchers to identify finer resolution statistically significant differences between groups of individuals. 
Mutations associated to a disease can be identified by comparing the genomes of healthy individuals to those afflicted by a disease. 
The mutations commonly found in patients and rarely in controls might be associated to the disease in question.
However, demonstrating that these mutations are biologically relevant can be difficult.
Especially with the increasing size of cohorts, spurious associations are increasingly becoming an issue. 
For this reason, careful consideration must be taken when including individuals from different ancestral origins in these association studies.
Benign mutations at high frequencies in one populations might be exceedingly rare in another population.
Therefore, population wide differences in mutations must be included as covariates to avoid spurious associations.

@@

Imputation of genotype data is a probabilistic method that infers the bases of a given genome based on its similarity to a set of reference genomes.
While on average, two humans differ in about 1/10,000 bases, this number is \todo{lower} in closely related individuals, and \todo{higher} in individuals from different continental origins.
Modern chip sequencing will provide the genotype information for over 1 million bases of the genome.
The unique combination of genotyped bases can be enough to identify haplotype blocks that are identical by descent in individuals form the reference database.

@@

>>>>

\author[1,2]{Luke Anderson-Trocm\'e}
\author[1,2]{Simon Gravel}

@@

\corr{simon.gravel@mcgill.ca}{SG}

@@

			\section{Introduction}
	\subsection{Reference Cohorts}			
The last 5 years has seen an increase in the number of individuals genotyped through private companies or medical research cohorts. 
Larger sample sizes allow researchers to identify finer resolution statistically significant differences between groups of individuals. 
Mutations associated to a disease can be identified by comparing the genomes of healthy individuals to those afflicted by a disease. 
The mutations commonly found in patients and rarely in controls might be associated to the disease in question.
However, demonstrating that these mutations are biologically relevant can be difficult.
Especially with the increasing size of cohorts, spurious associations are increasingly becoming an issue. 
For this reason, careful consideration must be taken when including individuals from different ancestral origins in these association studies.
Benign mutations at high frequencies in one populations might be exceedingly rare in another population.
Therefore, population wide differences in mutations must be included as covariates to avoid spurious associations.

@@

\luke{cut paragraph to discussion}

@@

\subsection{Imputation}
Imputation of genotype data is a probabilistic method that infers the bases of a given genome based on its similarity to a set of reference genomes.
While on average, two humans differ in about 1/10,000 bases, this number is \todo{lower} in closely related individuals, and \todo{higher} in individuals from different continental origins.
Modern chip sequencing will provide the genotype information for over 1 million bases of the genome.
The unique combination of genotyped bases can be enough to identify haplotype blocks that are identical by descent in individuals form the reference database.
